### 2023-06-12 Article.Rmd
1

Akin to Facebook, the sentiment indicator on Instagram averaged at 0.12, which points towards a mildly positive sentiment, with the spectrum extending from -0.22 to 0.46. The mean sentiment score for negatively perceived discourse was -0.07, and the positively perceived discourse showed an average of 0.20, once again suggesting a bend towards positive discourse on this platform.

Conversely, Twitter displayed a broader sentiment spectrum. Although the sentiment indicator mean was marginally higher than Facebook and Instagram at 0.15, it ranged from -0.63 to 1.00, implying a more diverse expression of sentiments. Negative discourse manifested an average of -0.07, identical to Instagram but more negative than Facebook. Interestingly, Twitter maintained the highest average score for positive discourse, at 0.22, equal to the positivity in Facebook and surpassing that on Instagram.

On YouTube, the sentiment indicator's mean value was observed to be the lowest amongst the evaluated platforms at 0.10, spanning from -0.19 to 0.34, thereby indicating a more tempered sentiment. Negative discourse on YouTube scored the lowest mean of -0.03, while positive discourse registered the minimum average of 0.13 compared to the other platforms.

>>>>

In contrast to Facebook, the sentiment indicator on Instagram averaged at `r ig.sent.mean.next`, which points towards a mildly positive sentiment, with the spectrum extending from `r ig.sent.min.next` and `r ig.sent.max.next` (`r ig.sent.min.ext` and `r ig.sent.max.ext` with extreme outliers). The mean sentiment score for negatively perceived discourse was `r ig.neg.mean.next` (SD=`r ig.neg.sd.next`), and the positively perceived discourse showed an average of (M=`r ig.neg.mean.ext`, SD=`r ig.neg.sd.ext`, respectively M=`r ig.poz.mean.ext`, SD=`r fb.poz.sd.ext` with extreme outliers), once again suggesting a bend towards positive discourse on this platform.

Conversely, Twitter displayed a broader sentiment spectrum. Although the sentiment indicator mean was marginally higher than Facebook and Instagram at `r tw.sent.mean.next`, it ranged from `r tw.sent.min.next` and `r tw.sent.max.next` (`r tw.sent.min.ext` and `r tw.sent.max.ext` with extreme outliers), implying a more diverse expression of sentiments. Negative discourse manifested an average of `r tw.neg.mean.next` (SD=`r tw.neg.sd.next`), identical to Instagram but more negative than Facebook. Interestingly, Twitter maintained the highest average score for positive discourse, at `r tw.poz.mean.ext` (SD=`r tw.poz.sd.ext` with extreme outliers), equal to the positivity in Facebook and surpassing that on Instagram.

On YouTube, the sentiment indicator's mean value was observed to be the lowest amongst the evaluated platforms at `r yt.sent.mean.next`, spanning from `r yt.sent.min.next` and `r yt.sent.max.next` (`r yt.sent.min.ext` and `r yt.sent.max.ext` with extreme outliers), thereby indicating a more tempered sentiment. Negative discourse on YouTube scored the lowest mean of `r yt.neg.mean.next` (SD=`r yt.neg.sd.next`), while positive discourse registered the minimum average of `r yt.poz.mean.ext` (SD=`r yt.poz.sd.ext` with extreme outliers) compared to the other platforms.
